Delving into the World Inside Prisons for Safety, Health, and Isolation

### 2024-02-11 outputs/paper/paper.qmd
change

According to the chart (@fig-planes), when comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges. In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.

@@

>>>>

When comparing the overall new coronavirus infection rate among the American population with the new coronavirus infection rate among prison inmates, a clear trend emerges according to the chart (@fig-planes). In the majority of states in the United States, the data pertaining to infection rates among prison inmates surpasses that of the general population by a significant margin.

@@

\ @novisky2020institutional indicates that the implementation of varied epidemic prevention policies across different states in the United States, alongside differences in the infrastructure of state prisons, has resulted in significant disparities in prisoner infection rates.
